---
title: "Code for conference debrief"
output:
  html_document: default
  html_notebook: default
---

```{r}
library(tidyverse)
library(repurrrsive)
# devtools::install_github("jennybc/repurrrsive")
```

## Tibbles


### 1. No coercing strings to characters
```{r}
(letters <- c(letters[1:10]))

(letters_df <- data.frame(letters = letters))

(letters_df <- data.frame(letters = letters, stringsAsFactors = FALSE))

(letters_tbl <- tibble(letters)) # The same as dplyr::data_frame
```

### 2. Stable subsetting

```{r}
(df1 <- data.frame(x = 1:3, y = 3:1))

df1[, 1:2]

df1[, 1]

df1[, 1, drop = FALSE]

df2 <- tibble(x = 1:3, y = 3:1)

df2[, 1:2]

df2[, 2]

df2[, 1]

class(df2[, 1])
```


### 3. No partial Matching

```{r}
(lazy_df <- data.frame(names = c("Hadley", "Garret", "Joe"),
                      course = c("Master R", "Tidyverse", "Shiny")))

lazy_df$na

(surly_tibble <- tibble(names = c("Hadley", "Garret", "Joe"),
                      course = c("Master R", "Tidyverse", "Shiny")))

surly_tibble$na
```

### 3. List columns!!

```{r}
data.frame(x = 1:3, y = list(1:5, 1:10, 1:20))

tibble(x = 1:3, y = list(1:5, 1:10, 1:20))
```


### 4. Evaluates arguments lazily and sequentially
```{r}
data.frame(x = 1:5, y = x ^ 2)

data.frame(x = 1:5) %>% 
  mutate(y = x ^ 2)

tibble(x = 1:5, y = x ^ 2)
```

## Functional Programming

### Warm ups:

What does this function return?

```{r}
y <- 10

g <- function() {
    x <- 5
    c(x = x, y = y)
}

g()
```


What does this function return the first time? the second time?
```{r}
j <- function() {
    if (!exists("a")) {
        a <- 5
    } else {
        a <- a + 1
    }
    a
}

j()

j()
```

Function runs are independent. They start always with a clean slate!
 
How many positions have NA in both vectors??
 
```{r}
# Write code to determine how many positions
# have an NA in both vectors.
x <- c(1, 1, NA, NA)

y <- c(1, NA, 1, NA)
```


```{r}
# Think about positions
which(is.na(x))

which(is.na(y))

intersect(which(is.na(x)), which(is.na(y)))

length(intersect(which(is.na(x)), which(is.na(y))))

# OR
 
sum(which(is.na(x)) %in% which(is.na(y)))
```

```{r}
# Boolean algebra
is.na(x) & is.na(y)

sum(is.na(x) & is.na(y))
```


```{r}
# after solving the problem make a function to generalize!

both_na <- function(x, y) {
  sum(is.na(x) & is.na(y))
}

both_na(x, y)
```

### Why write functions?
### Good functions

#### Fail fast 
```{r}
x <- c(1,NA)
y <- c(1,2,NA,NA)
both_na(x, y)
```


```{r}
both_na <- function(x, y) {
  stopifnot(length(x) == length(y))
  sum(is.na(x) & is.na(y))
}

both_na(x, y)
```

```{r}
both_na <- function(x, y) {
  if (length(x) != length(y))
    stop("`x` and `y` must be the same length.")
    stop("`x` and `y` are different lengths.")
  sum(is.na(x) & is.na(y))
}

both_na(x,y)
```

## For loops (back to slides)
## Functional programming

```{r}
set.seed(1014)
l <- rerun(20, runif(sample(1:10, 1)))
str(l)
```

```{r}
l[1]

l[2:5]

l[[10]]
```


```{r}
compute_length <- function(x) {
  out <- numeric(length(x))
  for (i in seq_along(x)) {
    out[[i]] <- length(x[[i]])
  }
out }

compute_length(l)
```

```{r}
compute_mean <- function(x) {
  out <- numeric(length(x))
  for (i in seq_along(x)) {
    out[[i]] <- mean(x[[i]])
  }
out }
```

```{r}
compute_median <- function(x) {
  out <- numeric(length(x))
  for (i in seq_along(x)) {
    out[[i]] <- median(x[[i]])
  }
out }
```

```{r}
compute <- function(x, f) {
  out <- numeric(length(x))
  for(i in seq_along(x)) {
    out[[i]] <- f(x[[i]])
  }
out }

compute(l, length)
compute(l, mean)
compute(l, median)
```

We have just created something very similar to sapply()

```{r}
sapply(l, length)
```

But... purrr map() functions are better :)

```{r}
map_dbl(l, length)
map_dbl(l,mean)
```

Why not lapply?

### type stable

```{r}
df <- data.frame(
  a = 1L,
  b = 1.5,
  y = Sys.time(),
  z = ordered(1)
)

df[1:4] %>% 
  sapply(class) %>% 
  str()

df[1:2] %>% 
  sapply(class) %>% 
  str()

df[3:4] %>% 
  sapply(class) %>% 
  str()
```

```{r}
col_means <- function(df) {
  numeric <- sapply(df, is.numeric)
  numeric_cols <- df[, numeric]
  data.frame(lapply(numeric_cols, mean))
}
```


```{r}
col_means(mtcars)

col_means(mtcars[, "mpg", drop = F])

df <- data.frame(x = 1:26, y = letters)

col_means(df)

map_dbl(mtcars, mean)
map_dbl(df, mean)
```

```{r}
col_means <- function(df) {
  stopifnot(is.data.frame(df))
  
  numeric <- map_lgl(df, is.numeric)
  numeric_cols <- df[, numeric, drop = FALSE]
  data.frame(lapply(numeric_cols, mean))
}
```

```{r}
col_means <- function(df) {
  stopifnot(is.data.frame(df))
  df %>%
    purrr::keep(is.numeric) %>%
    purrr::map(mean) %>%
    as.data.frame()
}
```

### Syntax and shortcuts (go to slides) 


```{r}
library(repurrrsive)

got_people <- got_chars
```

#### How many nicknames each character has?

```{r}
theon <- got_people[[1]]

length(theon$aliases)

tyrion <- got_people[[2]]

length(tyrion$aliases)

```

##### Turn it into a formula: `~ length(.x$aliases)`

```{r}
purrr::map(got_people, ~ length(.x$aliases)) 

purrr::map_dbl(got_people, ~ length(.x[["aliases"]]))  %>% 
  purrr::set_names(map_chr(got_people, ~.x$name))
```

##### map() can also take character strings!

```{r}
map_lgl(got_people, "alive") %>% 
  purrr::set_names(map_chr(got_people, "name")) %>% 
  keep(isTRUE) 
```

##### map() can also take character integers

```{r}
map_chr(got_people, 5) %>% 
  purrr::set_names(map_chr(got_people, "name")) 
```

#### purr and list columns

```{r}
x <- tibble(
  name = got_chars %>% map_chr("name"),
  aliases = got_chars %>% map("aliases"),
  allegiances = got_chars %>% map("allegiances")
)
```

```{r}
x <- x %>% 
  mutate(lannister = map(allegiances, stringr::str_detect, pattern = "Lannister"),
         lannister = map_lgl(lannister, any))
```


#### Handling errors

```{r}
input <- list(1:10, sqrt(4), 5, "1")

map(input, log)

map(input, safely(log)) 

results <- input %>% 
  map(safely(log)) %>% 
  transpose()
  
ok <- map_lgl(results$error, is.null)

ok

input[ok]
```


## the power of all combined
```{r}
monthly_effort_by_vessel <- readRDS("monthly_effort_by_mmsi")
```

```{r}
monthly_effort_by_vessel %>% 
  group_by(date, country) %>%
  summarise(total_distance_traveled = sum(distance_traveled)) %>% 
  arrange(date) %>%
  ggplot(aes(x = date, y = total_distance_traveled)) +
  geom_smooth() +
  geom_path() +
  theme_minimal() +
  facet_wrap(~ country)
```

```{r}
#devtools::install_github("hafen/trelliscopejs")
monthly_effort_by_vessel %>% 
  group_by(date, country) %>%
  summarise(total_distance_traveled = sum(distance_traveled)) %>% 
  arrange(date) %>%
  ggplot(aes(x = date, y = total_distance_traveled)) +
  geom_smooth() +
  geom_path() +
  theme_minimal() +
  trelliscopejs::facet_trelliscope(~country)
```

```{r}
nested_monthly_df <- monthly_effort_by_vessel %>%
  filter(!is.na(country)) %>% 
  group_by(country) %>% 
  nest()

nested_monthly_df
```

```{r}
detrending_model <- function(my_data){
  lm(distance_traveled ~ factor(lubridate::month(date)), data = my_data)
}

detrended_nested_monthly_df <- nested_monthly_df %>% 
  mutate(detrended_model = map(data, detrending_model))

detrended_nested_monthly_df

detrended_nested_monthly_df$detrended_model[[1]]
```

```{r}
detrended_nested_monthly_df <- detrended_nested_monthly_df %>% 
  mutate(residuals = purrr::map2(data, detrended_model, modelr::add_residuals, "residuals"))
```

```{r}
detrended_plot <- function(detrended_df){
  ggplot(detrended_df) +
    geom_path(aes(x = date, y = residuals)) +
    geom_smooth(aes(x = date, y = residuals))
}

detrended_nested_monthly_df <- detrended_nested_monthly_df %>% 
  mutate(plot = trelliscopejs::map_plot(residuals, detrended_plot))

detrended_nested_monthly_df %>%
  trelliscopejs::trelliscope(name = "plot")
```


```{r}
detrended_nested_monthly_df %>% 
  mutate(summary = map(detrended_model,broom::glance)) %>% 
  unnest(summary)
```


## Crosstalk

```{r}
# devtools::install_github("rstudio/crosstalk")
# devtools::install_github("jcheng5/d3scatter")
# devtools::install_github("rstudio/leaflet")
```


```{r}
library(leaflet)
library(tidyverse)
library(crosstalk)
library(d3scatter)


map <- leaflet(quakes, width = "100%", height = 300) %>%
    addTiles() %>%
    addMarkers()

plot <- d3scatter::d3scatter(quakes, ~depth, ~mag, width = "100%")

crosstalk::bscols(
  plot,
  map
)

shared_quakes <- crosstalk::SharedData$new(quakes[sample(nrow(quakes), 100),])


crosstalk::bscols(
  leaflet(shared_quakes, width = "100%", height = 300) %>%
    addTiles() %>%
    addMarkers(),
  d3scatter::d3scatter(shared_quakes, ~depth, ~mag, width = "100%")
)
```


```{r}
shared_iris <- SharedData$new(iris)

bscols(
  d3scatter(shared_iris, ~Petal.Length, ~Petal.Width, ~Species, width="100%", height=300),
  d3scatter(shared_iris, ~Sepal.Length, ~Sepal.Width, ~Species, width="100%", height=300)
)
```

```{r}
shared_mtcars <- SharedData$new(mtcars)

bscols(widths = c(3,NA,NA),
  list(
    filter_checkbox("cyl", "Cylinders", shared_mtcars, ~cyl, inline = TRUE),
    filter_slider("hp", "Horsepower", shared_mtcars, ~hp, width = "100%"),
    filter_select("auto", "Automatic", shared_mtcars, ~ifelse(am == 0, "Yes", "No"))
  ),
  d3scatter(shared_mtcars, ~wt, ~mpg, ~factor(cyl), width="100%", height=250),
  d3scatter(shared_mtcars, ~hp, ~qsec, ~factor(cyl), width="100%", height=250)
)
```

### Tesseract

```{r}
install.packages("tesseract")

text <- tesseract::ocr("tesseract_test.png")
cat(text)
```

### Corrr

```{r}
devtools::install_github("drsimonj/corrr")

library(corrr)

x <- mtcars %>%
       correlate() %>%    # Create correlation data frame (cor_df)
       focus(-cyl, -vs, mirror = TRUE) %>%  # Focus on cor_df without 'cyl' and 'vs'
       rearrange() %>%  # rearrange by correlations
       shave() # Shave off the upper triangle for a clean result


rplot(x)

airquality %>%
       correlate() %>% 
  network_plot(min_cor = .2, legend = TRUE)
```

